Twists of supersymmetric gauge theories

### 2019-11-19 paper.tex
more tidying in 6 and 5d

\subsubsection{$\mc N = (1,0)$ with hypermultiplet matter}

@@

In the 6 dimensional $\mc N=(1,1)$ supersymmetry algebra, there are now 4 classes of inequivalent non-zero supercharges by which we can twist.
\begin{enumerate}
 \item Rank $(1,0)$ spinors, $Q^+ \otimes w^+$.  These automatically square to zero, and are holomorphic, like in the $\mc N=(1,0)$ supersymmetry algebra.
 \item Rank $(1,1)$ spinors, $Q = Q^+ \otimes w^+ + Q^- \otimes w^-$.  These automatically square to zero, and split into two inequivalent classes:
 \begin{enumerate}
 \item \chris{4 invariant directions}
 \item \chris{topological (this twist is a degeneration of the previous type)}
 \end{enumerate}
 \item Rank $(2,2)$ square-zero spinors.  These supercharges have 5-dimensional image in $\CC^6$.  The corresponding twists are only $\ZZ/2\ZZ$-graded.
\end{enumerate}

@@

\chris{types 2a and 2b fit into a family of the form $\mr{Map}(S_2 \times \Sigma_{\mr{dR}}, BG)_{\mr{Hod}}$.  Type 3 gives $\mr{Map}(\Sigma \times (M_4)_{\mr{dR}}, BG)$.}

@@

\subsubsection{$\mc N = 1$ Super Yang-Mills with a Hypermultiplet}

@@

Exactly as in the case of 6d $\mc N=(1,1)$ supersymmetry algebra, there are 4 inequivalent classes of twists.
\begin{enumerate}
 \item Rank $1$ spinors, $Q \otimes w$.  These automatically square to zero, and admit three invariant directions.  Twists by such supercharges were already described in the previous subsection.
 \item Rank $2$ square-zero spinors.  Like in dimension 6, these split into two inequivalent classes:
 \begin{enumerate}
 \item \chris{4 invariant directions}
 \item \chris{topological (this twist is a degeneration of the previous type)}
 \end{enumerate}
 \item Rank $4$ square-zero spinors.  These supercharges are also topological.  The corresponding twists are only $\ZZ/2\ZZ$-graded.
\end{enumerate}

\chris{types 2a and 2b fit into a family of the form $\mr{Map}(\Sigma \times (M_3)_{\mr{dR}}, BG)_{\mr{Hod}}$.  Type 3 gives $\mr{Map}((M_5)_{\mr{dR}}, BG)$.}

>>>>

\subsubsection{$\mc N = (1,0)$ Super Yang-Mills Theory with Matter}

@@

In the 6 dimensional $\mc N=(1,1)$ supersymmetry algebra, there are now 4 classes of inequivalent non-zero supercharges by which we can twist.
\begin{enumerate}
 \item Rank $(1,0)$ spinors, $Q^+ \otimes w^+$.  These automatically square to zero, and are holomorphic.  Such supercharges factor through a copy of the $\mc N=(1,0)$ supersymmetry algebra.
 \item Rank $(1,1)$ spinors, $Q = Q^+ \otimes w^+ + Q^- \otimes w^-$.  These automatically square to zero, and split into two inequivalent classes:
 \begin{enumerate}
 \item Generically, $Q$ is topological.
 \item There is a degenerate locus where $Q$ has 4 invariant directions.  The former class can be realised as a degeneration of this case.
 \end{enumerate}
 \item Rank $(2,2)$ square-zero spinors.  These supercharges have 5-dimensional image in $\CC^6$.  The corresponding twists are only $\ZZ/2\ZZ$-graded.
\end{enumerate}

@@

\begin{theorem} \label{6d_rk11_twist_thm}
The twist of 6d $\mc N=(1,1)$ super Yang-Mills theory by a rank $(1,1)$ supercharge with 4 invariant directions on the product of a Calabi-Yau surface $S$ and an oriented 2-manifold $\Sigma$ is equivalent to mixed BF theory on the product $S \times \Sigma_{\mr{dR}}$. This twist degenerates to a one-parameter family of topological twists of the form $\map(S \times \Sigma_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
\end{theorem}

\begin{theorem} \label{6d_rk22_twist_thm}
The twist by a rank $(2,2)$ supercharge of 6d $\mc N=(1,1)$ super Yang-Mills theory on the product of a Calabi-Yau curve $C$ with an oriented 4-manifold $M_4$ is equivalent to mixed Chern-Simons theory on $C \times (M_4)_{\mr{dR}}$.
\end{theorem}

@@

\subsubsection{$\mc N = 1$ Super Yang-Mills Theory with Matter}

@@

Exactly as in the case of the 6d $\mc N=(1,1)$ supersymmetry algebra, there are 4 inequivalent classes of twists.
\begin{enumerate}
 \item Rank $1$ spinors, $Q \otimes w$.  These automatically square to zero, and admit three invariant directions.  Twists by such supercharges were already described in the previous subsection.
 \item Rank $2$ square-zero spinors.  Like in dimension 6, these split into two inequivalent classes:
 \begin{enumerate}
 \item Generically, $Q$ is topological.
 \item There is a special locus where $Q$ has 4 invariant directions.  The former class can be realised as a degeneration of this case.
 \end{enumerate}
 \item Rank $4$ square-zero spinors.  These supercharges are also topological.  The corresponding twists are only $\ZZ/2\ZZ$-graded.
\end{enumerate}

\begin{theorem} \label{5d_rk2_twist_thm}
The twist of 5d $\mc N=2$ super Yang-Mills theory by a rank $2$ supercharge with 4 invariant directions on the product of a Calabi-Yau curve $C$ and an oriented 3-manifold $M_3$ is equivalent to mixed BF theory on the product $C \times (M_3)_{\mr{dR}}$. This twist degenerates to a one-parameter family of topological twists of the form $\map(C \times (M_3)_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
\end{theorem}

\begin{theorem} \label{5d_rk4_twist_thm}
The twist by a rank $4$ supercharge of 5d $\mc N=2$ super Yang-Mills theory on ah an oriented 5-manifold $M_5$ is equivalent to 5d Chern-Simons theory on $M_5$.
\end{theorem}
